---
title: "Lab 02 - Plastic waste"
author: "Alex Connolly"
date: "01/26/2022"
output: github_document
---

## Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

```{r load-data, message=FALSE}
plastic_waste <- read.csv("data/plastic-waste.csv")
```

## Exercises

### Exercise 1


```{r plastic-waste-continent}
ggplot(data = plastic_waste, aes(x = plastic_waste_per_cap))+geom_histogram(binwidth = .2)

```
```{r plastic-waste-filter}
plastic_waste %>%
  filter(plastic_waste_per_cap>3.5)
```

Distributions of plastic waste per capita faceted by continent:

```{r plastic_continent}
ggplot(data = plastic_waste, aes(x=plastic_waste_per_cap))+geom_histogram()+facet_wrap(~continent)
```

Density plots:

```{r plastic-density}
ggplot(data=plastic_waste, aes(x= plastic_waste_per_cap)) + geom_density()
```

Distributions across continents

```{r plastic-distributions}
ggplot(data=plastic_waste, mapping = aes(x=plastic_waste_per_cap, color = continent))+ geom_density()
```

Overlapping colors:

```{r plastic-color}
ggplot(data=plastic_waste, mapping = aes(x=plastic_waste_per_cap, color = continent, fill = continent))+ geom_density()
```

Changing Transparency Levels:

```{r plastic-transparency}
ggplot(data=plastic_waste, mapping = aes(x=plastic_waste_per_cap, color= continent, fill=continent)) + geom_density(alpha=.7)
```


### Exercise 2

```{r plastic-new-alpha}
ggplot(data=plastic_waste, mapping = aes(x=plastic_waste_per_cap, color= continent, fill=continent)) + geom_density(alpha=.12)
```

The aesthetics of the plot control how the plot looks (color, fill), but changing  transparency is done as a characteristic of the plotting geom to be done on a more ???

Box Plot:

```{r plastic-box}
ggplot(data=plastic_waste, mapping = aes(x=continent, y=plastic_waste_per_cap))+geom_boxplot()

```


### Exercise 3

Remove this text, and add your answer for Exercise 3 here.

### Exercise 4

Remove this text, and add your answer for Exercise 4 here.

```{r plastic-waste-violin}
# insert code here
```

### Exercise 5

Remove this text, and add your answer for Exercise 5 here.

```{r plastic-waste-mismanaged}
# insert code here
```

### Exercise 6

Remove this text, and add your answer for Exercise 6 here.

```{r plastic-waste-mismanaged-continent}
# insert code here
```

### Exercise 7

Remove this text, and add your answer for Exercise 7 here.

```{r plastic-waste-population-total}
# insert code here
```

```{r plastic-waste-population-coastal}
# insert code here
```

### Exercise 8

Remove this text, and add your answer for Exercise 8 here.

```{r recreate-viz}
# insert code here
```

## Pro-Tips

### Excercise 3

Try this :D

ggplot(data = plastic_waste, 
       mapping = aes(x = continent, 
                     y = plastic_waste_per_cap)) +
  geom_violin()+
  geom_boxplot(width=.3, fill="green") +
  stat_summary(fun.y=median, geom="point") 
  
### Exercise 5 

Helpful reference:http://www.sthda.com/english/wiki/ggplot2-themes-and-background-colors-the-3-elements



