---
title: "Lab 02 - Plastic waste"
author: "Alex Connolly"
date: "01/26/2022"
output: github_document
---

## Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

```{r load-data, message=FALSE}
plastic_waste <- read.csv("data/plastic-waste.csv")
```

## Exercises

### Exercise 1


```{r plastic-waste-continent}
ggplot(data = plastic_waste, aes(x = plastic_waste_per_cap))+geom_histogram(binwidth = .2)

```
```{r plastic-waste-filter}
plastic_waste %>%
  filter(plastic_waste_per_cap>3.5)
```

Distributions of plastic waste per capita faceted by continent:

```{r plastic_continent}
ggplot(data = plastic_waste, aes(x=plastic_waste_per_cap))+geom_histogram()+facet_wrap(~continent)
```

Density plots:

```{r plastic-density}
ggplot(data=plastic_waste, aes(x= plastic_waste_per_cap)) + geom_density()
```

Distributions across continents

```{r plastic-distributions}
ggplot(data=plastic_waste, mapping = aes(x=plastic_waste_per_cap, color = continent))+ geom_density()
```

Overlapping colors:

```{r plastic-color}
ggplot(data=plastic_waste, mapping = aes(x=plastic_waste_per_cap, color = continent, fill = continent))+ geom_density()
```

Changing Transparency Levels:

```{r plastic-transparency}
ggplot(data=plastic_waste, mapping = aes(x=plastic_waste_per_cap, color= continent, fill=continent)) + geom_density(alpha=.7)
```


### Exercise 2

```{r plastic-new-alpha}
ggplot(data=plastic_waste, mapping = aes(x=plastic_waste_per_cap, color= continent, fill=continent)) +geom_density(alpha=.12)
```

If you try to put the alpha value within the aestethis, the plot dissapears completely, which i why we use it as a characteristic of a plotting geom.

Box Plot:

```{r plastic-box}
ggplot(data=plastic_waste, mapping = aes(x=continent, y=plastic_waste_per_cap))+geom_boxplot()

```


### Exercise 3

```{r violin-plots}
ggplot(data=plastic_waste, mapping = aes(x=continent, y=plastic_waste_per_cap))+ geom_violin()

```
This violin plot shows us more of the shape of the disstribution, whereas the box plots show us where the majority of the data lies, and outliers. 

### Exercise 4

```{r notcolor}
ggplot(data=plastic_waste, mapping = aes(x=mismanaged_plastic_waste,y=plastic_waste_per_cap))+ geom_point() 
```
The relationship would be linear except for two very obvious outliers, making it more like a left skewed relationship

```{r plastic-wasste-scatter}
ggplot(data=plastic_waste, mapping = aes(x=mismanaged_plastic_waste,color = continent,  y=plastic_waste_per_cap))+ geom_point() 

```

Its seems that the North American countries have higher waste per capita, with lower mismanged plastic waste, whereas the Asia countries have low plastic waste per capita but high mismanaged plastic waste.

```{r totalpop}
ggplot(data=plastic_waste, mapping = aes(x=total_pop,y=plastic_waste_per_cap))+ geom_point() 
```

```{r coastal-pop}
ggplot(data=plastic_waste, mapping = aes(x=coastal_pop,y=plastic_waste_per_cap))+ geom_point() 
```
It seems to me that coastal population apears to have a more linear relationship with palstic waste per capital than total population has. 
### Exercise 5


```{r plastic-vs-coastal}
plastic_waste %>%
  filter(plastic_waste_per_cap < 3.5) %>%
ggplot()+geom_smooth(mapping = aes(x=coastal_pop / total_pop,y = plastic_waste_per_cap)) + geom_point(mapping = aes(x=coastal_pop / total_pop,y = plastic_waste_per_cap, color = continent)) 

```




